DATA 621 - Business Analytics and Data Mining

### 2020-11-29 HW5/HW5-Group2.Rmd
Minor correction

```{r readEval}
# Read evaluation but not "IN" since that's dropped right away
m2eval <- fread(paste0(urlRemote, pathGithub, fileEval), drop = 'IN')
nobsE <- dim(DT)[[1]]
```

@@

```{r processEval}
# Process evaluation file as per zero-inflated Poisson model 2
m2eval[,c(2:8,11:12)] <- abs(m2eval[,c(2:8,11:12)])
m2eval$STARS[is.na(m2eval$STARS)] <- 0
set.seed(525)
m2eval.impute <- mice(m2eval, method = 'pmm', print = FALSE)
m2eval <- complete(m2eval.impute)
m2eval.r <- m2eval$TARGET
m2eval.p <- m2eval[, -1]
pre.process <- preProcess(m2eval.p, method = c("YeoJohnson"))
m2eval.p <- predict(pre.process, m2eval.p)
m2eval[, c(2:13, 15)] <- m2eval.p[, c(1:12, 14)]

>>>>

```{r readEval}
# Read evaluation but not "IN" since that's dropped right away
m2eval <- fread(paste0(urlRemote, pathGithub, fileEval), drop = 'IN')
nobsE <- dim(m2eval)[[1]]
```

@@

```{r processEval}
# Process evaluation file as per zero-inflated Poisson model 2
m2eval[, c(2:8, 11:12)] <- abs(m2eval[, c(2:8, 11:12)])
m2eval$STARS[is.na(m2eval$STARS)] <- 0
set.seed(525)
m2eval.impute <- mice(m2eval, method = 'pmm', print = FALSE)
m2eval <- complete(m2eval.impute)
m2eval.r <- m2eval$TARGET
m2eval.p <- m2eval[, -1]
pre.process <- preProcess(m2eval.p, method = c("YeoJohnson"))
m2eval.p <- predict(pre.process, m2eval.p)
m2eval[, c(2:13, 15)] <- m2eval.p[, c(1:12, 14)]
